\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{color,hyperref,url,keystroke}

\title{Simple Interactive Multiple Programming Language Learner (SIMPLL)}
\author{B. A. Bhathiya N. H. Perera}

\begin{document}
\maketitle

\begin{abstract}
SIMPLL pronounced “simple” is a set of batch files (windows cmd) and other bundled third party products which let you start learning multiple programming languages using interactive shells (or as some say interactive interpreters).
\end{abstract}

\section{Introduction}

SIMPLL was created in order for new developers to learn multiple programming/scripting languages rather easily using interactive shells (or interpreters). The main approach of this project is to ensure that the end users don’t need to worry about downloading ton of files and setting up the system before start learning a programming/scripting language. SIMPLL enables you to jump start your learning process in not just one but multiple programming/scripting languages. All you need to do is download a file and install or extract it and all is complete.

\section{How to Invoke an Interactive Shell ?}

\begin{enumerate}
\item Extract Bundle.
\item Run \texttt{Start.cmd} by double clicking.
\item Input \texttt{\textless Language\textgreater Start} and press Enter Key(\Return).
\end{enumerate}

\begin{itemize}
\setlength{\itemindent}{+.5in}
\item For Java : \texttt{JavaReplStart}
\item For Groovy : \texttt{GroovyStart}
\item For BASH : \texttt{BASHStart}
\item For Python : \texttt{PythonStart}
\item For Ruby : \texttt{RubyStart}
\item For C++ : \texttt{IGCCStart}
\end{itemize}

\section{Frequently Asked Questions (FAQ)}


\subsection{What are the Languages Available?}

Current version of SIMPLL comes with C++, Java, Groovy, Ruby and Python.  (Additionally Busybox can ensure you can learn BASH as well).


\subsection{What are the Bundled Third Party Products?}

\begin{enumerate}
\item MinGW Compiler
\item Open JDK 7
\item JavaREPL
\item Groovy
\item JRuby
\item JPython
\item IGCC
\item Busybox-w32 
\end{enumerate}


\subsection{What operating systems are supported?}
SIMPLL currently supports Windows only. However in the future versions there is a chance for implementing Linux version as well. It is possible since Jython,Groovy and JRuby runs on JVM and GCC is available for many platforms.

\subsection{What operating systems did you test SIMPLL?} 

\begin{enumerate}
\item Windows 7 Home Premium SP1 
\item Windows XP Professional SP3
\end{enumerate}

\subsection{How to contact the developer?}
Please send an email to \href{mailto:bhathiya91@live.com}{bhathiya91@live.com} or do a pull request in github repository \url{https://github.com/JaDogg/SIMPLL/}.


\end{document}